---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MATSSforecasting

## Overview

MATSSforecasting is a research compendium for investigationg different approaches to forecasting ecological time series. It implements multiple methods to forecasting single time series, as well as metrics of time series complexity, with the goal of synthesizing the results to provide guidance on forecasting methods.

## Running the code

Much of the underlying support code comprises the `MATSSforecasting` package, while the analysis code is in the analysis folder. Here is the suggested workflow for running the analysis.

1. Download or clone the entire repository.
2. Build and Install the package locally.
3. Run `main.R` in the `analysis` folder.

Alternatively, you can install `MATSSforecasting` from github with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ha0ye/MATSS-forecasting")
```

and then obtain just the `analysis` subfolder, and run `main.R`.
